---
title: "New York City 2019 Airbnb Data Analysis Report"
author: "Karan Dassi, Marzuq Khan, Amy Lu"
date: "December 11, 2019"
output: 
  pdf_document:
always_allow_html: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(tidyverse)
library(tigris)
library(leaflet)
library(sp)
library(ggmap)
library(maptools)
library(broom)
library(httr)
library(rgdal)
library(pdist)
library(webshot)
```


## New York Airbnb 2019

New York is one of the most popular spot for tourists around the world. Airbnb has been changing the way tourists travel. Therefore, our team would like to explore the Airbnbs in New York City in 2019. Our project will start with descriptive analysis of the data, exploratory data analysis and then a creation of a Shiny App.

By creating a Shiny dashboard, we can visually understanding where the rentals are, how much each rental is, type of rentals are and the availability of each rental within the city.

With our dashboard, tourists can review and select the rentals that they are interested in, based on their needs. We also want to incorporate the NY subway dataset to the AirBnB dataset so that we can see which rentals are closer or farther from subway stops.

- `id`: listing ID
- `name`: name of the listing
- `host_id`: host ID
- `host_name`: name of the host
- `neighbourhood_group`: location
- `neighbourhood`: area
- `latitude`: latitude coordinates
- `longitude`: longitude coordinates
- `room_type`: listing space type
- `price`: price in dollars
- `minimum_nights`: amount of nights minimum
- `number_of_reviews`: number of reviews
- `last_review`: latest review
- `reviews_per_month`: number of reviews per month
- `calculated_host_listings_count`: amount of listing per host
- `availability_365`: number of days when listing is available for booking

## Read Data

```{r}
airbnb <- read_csv("../data/AB_NYC_2019.csv")
glimpse(airbnb)
```

__Analysis:__ There are a total of 48,895 observations with 16 variables of rental and host id, rental name, neigourhood group, neighbourhood, longtitude, latitude, room type, price, minimum_nights, number of reviews received, most recent review date, number of reviews per month, calculated amount of listing per host and the number of day in availibility for booking in 2019.

```{r}
subway <- read_csv("../data/ny_subway.csv")
glimpse(subway)
```

__Analysis:__ There are 473 observations in the NY subway dataset with 6 variables of URL of each location's URL page, object ID, location name, longtitude, latitude, the subway lines of each location, and note which includes the train schedules.

## Cleaning the Subway Dataset


```{r}
subway %>%
  select(-URL) %>%
  mutate(the_geom = str_remove_all(string = the_geom, pattern = "POINT ")) -> subway
subway %>%
  mutate(setup = str_remove_all(string = the_geom, pattern = "\\(")) %>%
  mutate(setup = str_remove_all(string = setup, pattern = "\\)")) %>%
  mutate(longitude = str_remove_all(string = setup, pattern = " .*$"),
         latitude = str_remove_all(string = setup, pattern = "^.* ")) %>%
  mutate(latitude = as.numeric(latitude),
         longitude = as.numeric(longitude)) %>%
  select(OBJECTID, NAME, LINE, latitude, longitude) -> cleaned_subway
#saveRDS(object = cleaned_subway, file = "../data/clean_sub.RDS") ## Only need this line the first run

nysub <- read_rds("../data/clean_sub.RDS")
head(nysub)
```

# Exploratory Data Analysis

## Number of days the listing is available for booking in 2019

```{r}
airbnb%>%
  group_by(availability_365)%>%
  count()%>%
  ggplot(aes(x = availability_365, y = n)) +
  geom_col(fill = "#00A699") +
  theme_bw() +
  scale_y_log10() +
  xlab("Availability") +
  ylab("Number of Rentals")
```

__Findings:__ It seems there are various rentals available throughout the year. A good amount of the units seem to be booked with zero availability however, there are still many units can be rented through out the year.

## How popular Airbnb is by neighborhoods

We calculate the number of reviews across the neighborhoods to identify which location(s) have the most reviews (doesn't matter if it was positve or negative reviews, a review means a stay in the unit.)

```{r}
airbnb%>%
  group_by(neighbourhood_group)%>%
  summarise(total_review = sum(number_of_reviews))%>%
  mutate(percent_review = total_review/ sum(total_review)*100)%>%
  ggplot(aes(x = fct_reorder(neighbourhood_group, percent_review), y = percent_review)) +
  geom_col(fill = "#FF5A5F") +
  theme_bw() +
  ggtitle("Review Rate by Neighborhood Group") +
  xlab("Neighbouhood Group") +
  ylab("Review Rate") +
  coord_flip()
```

__Analysis:__ Based on the plot, Brooklyn has the highest review rate for more than 40% among all 5 neighbourhood groups, followed by Manhattan with approximately 40%. Brooklyn and Manhattan are the most popular neighborhood for renters.

## Listed price by neighbourhood_group

```{r}
airbnb%>%
  group_by(neighbourhood_group)%>%
  summarise(avg_price = mean(price))%>%
  ggplot(aes(x = fct_reorder(neighbourhood_group, avg_price), y = avg_price)) +
  geom_col(fill = "#FF5A5F") +
  theme_bw() +
  ggtitle("Rental Price by Neighborhood Group") +
  xlab("Neighbouhood Group") +
  ylab("Price") +
  coord_flip()
```

__Analysis:__ Manhattan has the highest average rental price among all other Neighbouhood groups by almost 1/3 more. Interestingly, rentals in other areas have similar average prices.


## Neighbourhood vs listed rental rate


```{r}
airbnb%>%
  group_by(neighbourhood_group)%>%
  summarise(sum_rental = sum(id))%>%
  mutate(percent_rental_count = sum_rental/ sum(sum_rental)*100)%>%
  ggplot(aes(x = fct_reorder(neighbourhood_group, percent_rental_count), y = percent_rental_count)) +geom_col(fill = "#FF5A5F") +
  theme_bw() +
  ggtitle("Availability by Neighborhood Group") +
  xlab("Neighbouhood Group") +
  ylab("Rental Rate") +
  coord_flip()
```

__Analysis:__ Around 80% list rentals are gathering in Manhattan and Brooklyn which we believe is expected as these two neighbouhood groups have the most attractions that tourists would be interested in, and have the most entertainment/ restaurants to explore.

## Neighbourhood vs availability

```{r}
airbnb%>%
  group_by(neighbourhood_group)%>%
  summarise(sum_avalibility = sum(availability_365))%>%
  mutate(percent_avai = sum_avalibility/ sum(sum_avalibility)*100)%>%
  ggplot(aes(x = fct_reorder(neighbourhood_group, percent_avai), y = percent_avai)) +
  geom_col(fill = "#FF5A5F") +
  theme_bw() +
  ggtitle("Availability Rate by Neighborhood Group") +
  xlab("Neighbouhood Group") +
  ylab("Availability Rate") +
  coord_flip()
```

__Analysis:__ Similar to the previous plot, most available rentals are also in Manhattan and Brooklyn.

## Type of rental

```{r}
airbnb%>%
  group_by(room_type)%>%
  count(name = "type_count")%>%
  ggplot(aes(x = fct_reorder(room_type, type_count), y = type_count)) +
  geom_col(fill = "#FF5A5F") +
  theme_bw() +
  ggtitle("Room Type Count") +
  xlab("Room Type") +
  ylab("Counts") +
  coord_flip()
```

__Analysis:__ Most rental types are either entire units or private rooms. Shared room has the least amount within the city.


## NYC map vs Airbnb rentals

```{r}
airbnb%>%
  group_by(neighbourhood_group)%>%
  mutate(sum_rental = n())%>%
  select(name, neighbourhood_group, latitude, longitude, sum_rental) -> airbnb_count



leaflet(airbnb_count) %>%
  addTiles() %>%
  setView(-74.00, 40.71, zoom = 12)%>%
  addMarkers(clusterOptions = markerClusterOptions(), label = ~as.character(name))
```

__Analysis:__ This is a quick glance of what we would like to explore on our Shiny App. We would like to incorporate the location of each Airbnb rental with the closest subway stations to each unit.

## Price versus Distance from Subway Stations

```{r}
airbnb %>%
  select(name, neighbourhood_group, latitude, longitude, price) -> airbnb_price

airbnb_loc <- tibble("lat" = airbnb_price$latitude, "long" = airbnb_price$longitude)

sub_loc <- tibble("lat" = nysub$latitude, "long" = nysub$longitude)

distmat <- as.matrix(pdist(X = airbnb_loc, Y = sub_loc))

airbnb_loc$min_dist_from_sub <- apply(distmat, 1, min)
bind_cols(airbnb_price, "near_sub" = (airbnb_loc$min_dist_from_sub*87)) -> airbnb_price
#saveRDS(airbnb_price, "../data/airbnb_price.RDS") ## Only need this line the first run

airbnb_price <- read_rds("../data/airbnb_price.RDS")
glimpse(airbnb_price)
leaflet(airbnb_price) %>%
  addTiles() %>%
  setView(-74.00, 40.71, zoom = 12)%>%
  addMarkers(clusterOptions = markerClusterOptions(), label = ~as.character(price))
```

__Analysis:__ This is mostly just set up and another look at what we improve on with the app.

## Exploring the reviews per neighborhood group to get popularity

```{r}
airbnb %>%
  group_by(neighbourhood_group) %>%
  summarise(sumReview = sum(number_of_reviews)) %>%
  ggplot(aes(x=fct_reorder(neighbourhood_group, sumReview), y=sumReview)) +
  geom_col(fill = "light blue", color = "black") +
  ylab("Total Reviews") +
  xlab("Neighborhood") +
  ggtitle("Neighborhood vs Total Reviews") +
  theme_bw()

airbnb %>%
  group_by(neighbourhood_group) %>%
  summarise(sumReview = sum(number_of_reviews)) %>%
  mutate(fracReview = sumReview/sum(sumReview)) %>%
  ggplot(aes(x=fct_reorder(neighbourhood_group, fracReview), y=fracReview)) +
  geom_col(fill = "light blue", color = "black") +
  ylab("Fraction of Total Reviews") +
  xlab("Neighborhood") +
  ggtitle("Neighborhood vs Fraction of Reviews") +
  theme_bw()

airbnb %>%
  select(neighbourhood_group, number_of_reviews) %>%
  group_by(neighbourhood_group) %>%
  count()
  
airbnb %>%
  select(neighbourhood_group, number_of_reviews) %>%
  group_by(neighbourhood_group) %>%
  summarise(sumofReviews = sum(number_of_reviews))



```

__Analysis:__ The above plots clearly show that Brooklyn and Manhattan have greater number of reviews in total.

## More exploration using reviews per month:  

```{r}

airbnb %>%
  group_by(neighbourhood_group) %>%
  summarise(meanReview = mean(reviews_per_month, na.rm = T)) %>%
  ggplot(aes(x=fct_reorder(neighbourhood_group, meanReview), y=meanReview)) +
  geom_col(color = "black", fill = "light blue") +
  ylab("Mean of Reviews per month") +
  xlab("Neighborhood") +
  ggtitle("Neighborhood vs Mean of Monthly Reviews") +
  theme_bw()

```

__Analysis:__ We believe the average of reviews per month is a better way of known which neighborhood groups have more reviews per month, here Queens, Staten Island and Bronx have the greater average amount of reviews per month.


## Explore: What role does minimum_nights play?

```{r}

airbnb %>%
  group_by(id) %>%
  count() %>%
  filter(n>1)
# So id is unique

glimpse(airbnb)

# Relation between minimum nights and price

airbnb %>%
  ggplot(aes(y=price, x=minimum_nights)) +
  geom_point(alpha = 1/3) +
  scale_x_log10() +
  xlab("Minimum number of nights") +
  ylab("Price") +
  geom_smooth(method = lm, se = F)

# Checking minimum nights

airbnb %>%
  arrange(-minimum_nights) %>%
  head(n=50) %>%
  select(name, host_name, price, minimum_nights)
airbnb %>%
  filter(minimum_nights > 90) %>%
  ggplot(aes(x=minimum_nights)) +
  geom_histogram(fill = "light blue", color = "black", bins = 15) +
  theme_bw()
```

__Analysis:__ It is interesting to note that many airbnb listings require over 3 months of minimum nights. Quite a few even require a full year's stay (365 minimum nights). One listing even requires 1250 minimum nights (~3.42 years), which is hard to believe. It is understandable that a host would like to have a steady income through renting out their property, however it seems unlikely many people would actually agree to stay for a minimum of over 1 year. Generally it does not seems to be the purpose of Airbnb to help people find long term housing, but it seems as though it can be used for that as well.

There is not a clear relationship between minimum number of nights required and price so we cannot safely say that the price decreases as the number of nights increases.

```{r}
# minimum nights vs room type
glimpse(airbnb)

airbnb %>%
  ggplot(aes(x=room_type, y=minimum_nights)) +
  geom_boxplot(fill = "light blue", color = "black") +
  scale_y_log10()
```

__Analysis:__ We can see that room type does affect minimum number of nights spent which is the lowest for shared rooms but highest for entire home/apt which also makes sense.

```{r}
glimpse(airbnb)

airbnb %>%
  ggplot(aes(x=neighbourhood_group, y=minimum_nights)) +
  geom_boxplot(fill = "light blue", color = "black") +
  scale_y_log10()
```

# Airbnb Shiny App

*We would recommend running the R file in the app folder for the best result as well as looking over the README file in that same folder for some insight on its applications*

```{r, eval=FALSE}
library(shiny)
library(DT)
library(tidyverse)
library(ggstance)
library(broom)
library(ggthemes)
library(leaflet)
library(shinythemes)
library(tigris)
library(sp)
library(maptools)
library(httr)
library(rgdal)
library(ui)
library(rsconnect)
library(plotly)

# Karan
airbnb <- read_csv("../data/AB_NYC_2019.csv")
airbnbd <- airbnb
airbnb %>%
  dplyr::select(-latitude, -longitude) ->
  airbnbR


# Marzuq
airbnb_price <- read_rds("../data/airbnb_price.RDS")
glimpse(airbnb_price)
nysub <- read_rds("../data/clean_sub.RDS")
glimpse(nysub)

# Amy
head(airbnb)
names(airbnb)[5] <- "borough"
airbnb <- airbnb%>%
  select(id, name, host_id, borough, latitude, longitude, room_type, price, number_of_reviews)%>%
  mutate(id = as.factor(id),
         host_id = as.factor(host_id))
borough <- c("Brooklyn", "Manhattan", "Queens", "Staten Island", "Bronx")
room_type <- c("Private room", "Entire home/apt", "Shared room")
pal <- colorFactor(c("#FF5A5F", "#00A699","#767676"), domain = c("Entire home/apt", "Private room","Shared room"))
max(airbnb$price)
min(airbnb$price)
max(airbnb$number_of_reviews)
min(airbnb$number_of_reviews)

ui <- fluidPage(shinythemes::themeSelector(),
                  fluidRow(
                  column(4,
                         titlePanel("New York City Airbnb")
                  ),
                  column(4
                  ),
                  column(4,
                         tags$img(src = "airbnb.png",  height = "60")
                  )
                ),
                tabsetPanel(
                  tabPanel("Dataset",
                           dataTableOutput("dt")
                  ),
                  tabPanel("Histograms",
                           sidebarLayout(
                             sidebarPanel(
                               varSelectInput("univar", "Variable to Plot", data = airbnbR, selected = "price"),
                               checkboxInput("unilog", "Log X"),
                               sliderInput("unibins", "Bins", min = 1, max = 100, value = 20),
                               numericInput("uninull", "Null Value", value = 0),
                               tableOutput("unitest_results")
                             ),
                             mainPanel(
                               plotOutput("hist")
                             )
                           )
                  ),
                  tabPanel("Plots",
                           sidebarLayout(
                             sidebarPanel(
                               varSelectInput("var1", "Variable X", data = airbnbR, selected = "neighbourhood_group"),
                               checkboxInput("var1log", "Log X"),
                               varSelectInput("var2", "Variable Y", data = airbnbR, selected = "price"),
                               checkboxInput("var2log", "Log Y"),
                               checkboxInput("ols", "OLS Line")
                             ),
                             mainPanel(
                               plotOutput("scatter")
                             )
                           )
                  ),
                  tabPanel(
                    "Price/Subway Map",
                    sidebarLayout(
                      sidebarPanel(
                        selectInput("var",
                                    label = "Airbnb or Subway?",
                                    choices = list("Airbnb", "Subway"), 
                                    selected = "Airbnb")
                      ),
                      mainPanel(
                        leafletOutput("PriceMap")
                      )
                    )
                  ),
                  tabPanel(
                    "Price/Distance Relationship",
                    sidebarLayout(
                      sidebarPanel(
                        checkboxInput("logx", "Log the Distance Variable"),
                        checkboxInput("logy", "Log the Price Variable"),
                        tableOutput("lmt"),
                        tableOutput("minT"),
                        tableOutput("maxT")
                      ),
                      mainPanel(
                        plotOutput("PDplot")
                      )
                    )
                  ),
                  tabPanel("Rental Finder",
                           div(class="outer",
                               leafletOutput("map"),
                               absolutePanel(
                                 column(3, checkboxGroupInput("borough","Neighborhood:",
                                                              choices = borough,
                                                              selected = borough),
                                        checkboxGroupInput("room_type","Room Type:",
                                                           choices = room_type,
                                                           selected = room_type),
                                        sliderInput("price", "Budget:", min = 0,  
                                                    max = 10000, value = c(0, 3000), step = 50),
                                        sliderInput("review", "Number of Reviews:", min = 0,
                                                    max = 629, value = c(0,200), step = 10)),
                                 column(5, plotOutput("plot1")),
                                 column(4, plotOutput("plot2")))
                           )
                  ),
                  tabPanel("Reference", textOutput("ref1"),
                           textOutput("ref2"),
                           textOutput("ref3")
                           )
                  )
                )


server <- function(input, output, session) {
  output$hist <- renderPlot({
    pl <- ggplot(airbnbR, aes(x = !!input$univar)) +
      theme_bw()
    
    if (is.numeric(airbnbR[[input$univar]])) {
      pl <- pl + geom_histogram(bins = input$unibins, fill = "light blue", color = "black")
      if (input$unilog) {
        pl <- pl + scale_x_log10()
      }
    } else {
      pl <- pl + geom_bar(fill = "light blue", color = "black")
    }
    
    pl
  })
  
  output$unitest_results <- renderTable({
    if (input$unilog & is.numeric(airbnbR[[input$univar]])) {
      airbnbR %>%
        mutate(logvar = log2(!!input$univar + 0.5)) -> temp
      t.test(temp[["logvar"]], mu = input$uninull) %>%
        tidy() %>%
        select(`P-value` = p.value,
               Lower = conf.low,
               Upper = conf.high)
    } else if (is.numeric(airbnbR[[input$univar]])) {
      t.test(airbnbR[[input$univar]], mu = input$uninull) %>%
        tidy() %>%
        select(`P-value` = p.value,
               Lower = conf.low,
               Upper = conf.high)
    } else {
      "Not a numeric"
    }
  })
  
  output$scatter <- renderPlot({
    airbnbR %>%
      ggplot(aes(x = !!input$var1, y = !!input$var2)) +
      theme_bw() ->
      pl
    if (is.numeric(airbnbR[[input$var1]]) & is.numeric(airbnbR[[input$var2]])) {
      pl <- pl + geom_point(color = "#FF5A5F")
    } else if (!is.numeric(airbnbR[[input$var1]]) & is.numeric(airbnbR[[input$var2]])) {
      pl <- pl + geom_boxplot(fill = "#00A699")
    } else if (is.numeric(airbnbR[[input$var1]]) & !is.numeric(airbnbR[[input$var2]])) {
      pl <- pl + geom_boxploth(fill = "#00A699")
    } else {
      pl <- pl + geom_jitter()
    }
    
    if (input$var1log & is.numeric(airbnbR[[input$var1]])) {
      pl <- pl + scale_x_log10()
    }
    
    if (input$var2log & is.numeric(airbnbR[[input$var2]])) {
      pl <- pl + scale_y_log10()
    }
    
    if (input$ols & is.numeric(airbnbR[[input$var1]]) & is.numeric(airbnbR[[input$var2]])) {
      pl <- pl + geom_smooth(se = FALSE, method = "lm")
    }
    
    pl
  })
  
  output$dt <- renderDataTable({
    airbnbd
  }, 
  options = list(pageLength = 10)
  )
  
  output$PriceMap <- renderLeaflet({
    if (input$var == "Airbnb") {
      leaflet(airbnb_price) %>%
        addTiles() %>%
        setView(-74.00, 40.71, zoom = 12)%>%
        addMarkers(clusterOptions = markerClusterOptions(), 
                   popup = ~paste("-Listing: ", name, 
                                  "-Subway Distance (miles): ", near_sub,
                                  sep = "<br/>"),
                   label = ~paste("Price: $",price))
    } else if (input$var == "Subway") {
      leaflet(nysub) %>%
        addTiles() %>%
        setView(-74.00, 40.71, zoom = 12)%>%
        addMarkers(clusterOptions = markerClusterOptions(), 
                   label = ~as.character(str_c("Subway Station: ", NAME)),
                   popup = ~as.character(str_c("Subway Line: ", LINE)))
    }
  })
  
  output$lmt <- renderTable({
    if (input$logx == TRUE & input$logy == FALSE) {
      newlm <- lm(price ~ log(near_sub), airbnb_price)
    } else if (input$logx == FALSE & input$logy == TRUE) {
      newlm <- lm(log(price + 1 - min(price)) ~ near_sub, airbnb_price)
    } else if (input$logx == TRUE & input$logy == TRUE) {
      newlm <- lm(log(price + 1 - min(price)) ~ log(near_sub), airbnb_price)
    } else {
      newlm <- lm(price ~ near_sub, airbnb_price)
    }
    tidy(newlm, conf.int = TRUE) %>%
      select(term, estimate, p.value) 
  })
  
  output$minT <- renderTable({
    airbnb_price %>%
      select("Min Price" = price) %>%
      arrange(`Min Price`) %>%
      head(n = 5) -> c1
    airbnb_price %>%
      select("Min Distance" = near_sub) %>%
      arrange(`Min Distance`) %>%
      head(n = 5) -> c2
    airbnb_price %>%
      mutate(pricel = log10(price + 1 - min(price))) %>%
      select("Min Price" = pricel) %>%
      arrange(`Min Price`) %>%
      head(n = 5) -> c3
    airbnb_price %>%
      mutate(near_subl = log10(near_sub)) %>%
      select("Min Distance" = near_subl) %>%
      arrange(`Min Distance`) %>%
      head(n = 5) -> c4
    
    if (input$logx == TRUE & input$logy == FALSE) {
      bind_cols(c4, c1)
    } else if (input$logx == FALSE & input$logy == TRUE) {
      bind_cols(c2, c3)
    } else if (input$logx == TRUE & input$logy == TRUE) {
      bind_cols(c4, c3)
    } else {
      bind_cols(c2, c1)
    }
  })
  
  output$maxT <- renderTable({
    airbnb_price %>%
      select("Max Price" = price) %>%
      arrange(-`Max Price`) %>%
      head(n = 5) -> c_1
    airbnb_price %>%
      select("Max Distance" = near_sub) %>%
      arrange(-`Max Distance`) %>%
      head(n = 5) -> c_2
    airbnb_price %>%
      mutate(pricel = log10(price + 1 - min(price))) %>%
      select("Max Price" = pricel) %>%
      arrange(-`Max Price`) %>%
      head(n = 5) -> c_3
    airbnb_price %>%
      mutate(near_subl = log10(near_sub)) %>%
      select("Max Distance" = near_subl) %>%
      arrange(-`Max Distance`) %>%
      head(n = 5) -> c_4
    
    if (input$logx == TRUE & input$logy == FALSE) {
      bind_cols(c_4, c_1)
    } else if (input$logx == FALSE & input$logy == TRUE) {
      bind_cols(c_2, c_3)
    } else if (input$logx == TRUE & input$logy == TRUE) {
      bind_cols(c_4, c_3)
    } else {
      bind_cols(c_2, c_1)
    }
  })
  
  output$PDplot <- renderPlot({
    airbnb_price %>%
      ggplot(aes(x=near_sub, y=price)) +
      geom_smooth(method = "lm", se = FALSE, color = "black") +
      geom_point(aes(color = neighbourhood_group)) +
      ylab("Rental Price (USD)") +
      xlab("Distance from Nearest Subway Station (Miles)") +
      labs(color = "Neighborhood") +
      theme_bw() -> pl
    
    airbnb_price %>%
      ggplot(aes(x=near_sub, y=log10(price + 1 - min(price)))) +
      geom_smooth(method = "lm", se = FALSE, color = "black") +
      geom_point(aes(color = neighbourhood_group)) +
      ylab("Rental Price (USD)") +
      xlab("Distance from Nearest Subway Station (Miles)") +
      labs(color = "Neighborhood") +
      theme_bw() -> nl
    
    airbnb_price %>%
      ggplot(aes(x=log10(near_sub), y=price)) +
      geom_smooth(method = "lm", se = FALSE, color = "black") +
      geom_point(aes(color = neighbourhood_group)) +
      ylab("Rental Price (USD)") +
      xlab("Distance from Nearest Subway Station (Miles)") +
      labs(color = "Neighborhood") +
      theme_bw() -> ol
    
    airbnb_price %>%
      ggplot(aes(x=log10(near_sub), y=log10(price + 1 - min(price)))) +
      geom_smooth(method = "lm", se = FALSE, color = "black") +
      geom_point(aes(color = neighbourhood_group)) +
      ylab("Rental Price (USD)") +
      xlab("Distance from Nearest Subway Station (Miles)") +
      labs(color = "Neighborhood") +
      theme_bw() -> ql
    
    if (input$logx == TRUE & input$logy == FALSE) {
      ol
    } else if (input$logx == FALSE & input$logy == TRUE) {
      nl
    } else if (input$logx == TRUE & input$logy == TRUE) {
      ql
    } else {
      pl 
    }
  })
  
  mapdata <- reactive({
    airbnb %>%
      filter(borough %in% input$borough,
             room_type %in% input$room_type,
             price >= input$price[1],
             price<= input$price[2],
             number_of_reviews >=input$review[1],
             number_of_reviews <=input$review[2])
  })
  
  output$map <- renderLeaflet({
    leaflet(mapdata()) %>%
      setView(lng = -73.94197, lat = 40.73638, zoom = 12) %>%
      addProviderTiles(providers$CartoDB.Positron) %>%
      addTiles()%>%
      addMarkers(clusterOptions = markerClusterOptions(),
                 popup = ~paste("Neighborhood:", borough,
                                "Room Type:", room_type,
                                "Budget:", price,
                                "Number of Reviews:", number_of_reviews,
                                sep = "<br/>"))
  })
  
  output$plot1 <- renderPlot({
    mapdata()%>%
      ggplot(aes(x = borough, y = price)) +
      geom_boxplot(fill = "#FF5A5F") +
      theme_bw() +
      xlab("Neighborhood") +
      ylab("Price") +
      scale_y_log10()
  })
  
  output$plot2 <- renderPlot({
    mapdata()%>%
      ggplot(aes(x = room_type, y = price)) +
      geom_boxplot(fill = "#00A699") +
      theme_bw() +
      xlab("Room Type") +
      ylab("Price") +
      scale_y_log10()
  })
  
  output$ref1 <- renderText("https://nycdatascience.com/blog/student-works/how-airbnb-is-in-nyc-interactive-data-visualization-in-r/")
  output$ref2 <- renderText("https://rstudio.github.io/leaflet/markers.html")
  output$ref3 <- renderText("https://usbrandcolors.com/airbnb-colors/")
}

shinyApp(ui, server)
```
